Data Management for LSST Special Programs

### 2023-10-19 sec_proc.tex
cross-ref to reqs

\item \textbf{Very short exposures --}
Special Programs which use very short ($<$2 sec) exposures 
could be difficult to reduce due to an incompletely-formed PSF 
(Section~\ref{ssec:procbounds_expt}).
The Data Management System is required to be able to process exposure 
times as low as 1 second, but it is known that such short exposures might 
have degraded image quality.

@@

\textbf{The meaning of ``can be processed".}
This is ultimately left to the discretion of
Rubin Data Management in Rubin Operations, but is expected to include
all standard and alternative visits in sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.
Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).

@@

\textbf{How WFD and Special Program data would co-reside.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the WFD program as 
described in Section 3 of the DPDD \citedsp{lse-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.

@@

These two potential issues pose challenges, but are not showstoppers in processing 
Special Programs data with the Prompt pipelines. 
The overall impact on time-domain science would still be positive, even 
if mitigations are needed for these issues.
For example, brokers and users would be able to use the region and program labels
in the data as context (i.e., as flags) and avoid including 
limited-history or potentially-compromised {\tt DiaSources} in their
analyses if necessary.

@@

As described in Section~\ref{ssec:sci_sproc}, 
Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.

@@

\textbf{Joinable tables --}
Any tables for the unique and separate data products should be joinable to the 
data products for the WFD program, when possible.

\textbf{Survey property maps --}
As for the tesslated all-sky coadded images made from WFD program data, survey property maps
should be made individually as part of any Special Programs that generates
tesselated coadded images.

>>>>

\item \textbf{Very short exposures --}
Special Programs which use very short ($<$2 sec) exposures 
could be difficult to reduce due to an incompletely-formed PSF 
(Section~\ref{ssec:procbounds_expt}).
The Data Management System is required to be able to process exposure 
times as low as 1 second (Section~\ref{ssec:req_proc}), 
but it is known that such short exposures might have degraded image quality.

@@

\textbf{The meaning of ``can be processed".}
This is ultimately left to the discretion of
Rubin Data Management in Rubin Operations, but is expected to include
all standard and alternative visits in sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.
Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).
Alert latency requirements do apply to Special Programs data (Section~\ref{ssec:req_proc}),
and if they cannot be met then Prompt processing is ``not possible".

@@

\textbf{How WFD and Special Program data would co-exist.}
No ``unique and separate" data products for the Special Progams would be 
produced by regular Prompt processing.
Special Programs data that is processed by the Prompt pipeline would 
contribute to the Prompt data products for the WFD program as 
described in Section 3 of the DPDD \citedsp{lse-163}. 
These data products are the results of Difference Image Analysis (DIA),
such as the difference images, catalogs of sources detected in difference
images ({\tt DiaSources}) and associated static-sky {\tt DiaSources}
into {\tt DiaObjects}, and alert packets.

@@

These two potential issues pose challenges, but are not necessarily showstoppers in processing 
Special Programs data with the Prompt pipelines. 
The overall impact on time-domain science would still be positive, even 
if mitigations are needed for these issues.
For example, brokers and users would be able to use the region and program labels
in the data as context (i.e., as flags) and avoid including 
limited-history or potentially-compromised {\tt DiaSources} in their
analyses if necessary.

@@

As described in Section~\ref{ssec:sci_sproc}, 
Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.
This is a requirement (Section~\ref{ssec:req_dp}).

@@

\textbf{Joinable tables --}
Any tables for the unique and separate data products should be joinable to the 
data products for the WFD program, when possible.
This is a requirement (Section~\ref{ssec:req_dp}).

\textbf{Survey property maps --}
As for the tesslated all-sky coadded images made from WFD program data, survey property maps
should be made individually as part of any Special Programs that generates
tesselated coadded images. This is \emph{not} a requirement (Section~\ref{ssec:req_dp}).
